%% ----------------------------------------------------------------
%% Thesis.tex -- MAIN FILE (the one that you compile with LaTeX)
%% ---------------------------------------------------------------- 

% Set up the document
\documentclass[a4paper, 11pt, oneside]{Thesis}  % Use the "Thesis" style, based on the ECS Thesis style by Steve Gunn
\usepackage{graphicx}
\graphicspath{ {images/} }
\usepackage{wrapfig}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}

% Include any extra LaTeX packages required
\usepackage{biblatex}
\addbibresource{Bibliography.bib}
\usepackage{verbatim}  % Needed for the "comment" environment to make LaTeX comments
\usepackage{vector}  % Allows "\bvec{}" and "\buvec{}" for "blackboard" style bold vectors in maths
\hypersetup{urlcolor=blue, colorlinks=true}  % Colours hyperlinks in blue, but this can be distracting if there are many links.
\usepackage{listings}
\usepackage{color}

\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}

\lstset{frame=tb,
  language=TCL,
  aboveskip=3mm,
  belowskip=3mm,
  showstringspaces=false,
  columns=flexible,
  basicstyle={\small\ttfamily},
  numbers=none,
  numberstyle=\tiny\color{gray},
  keywordstyle=\color{blue},
  commentstyle=\color{dkgreen},
  stringstyle=\color{mauve},
  breaklines=true,
  breakatwhitespace=true,
  tabsize=3
}

%% ----------------------------------------------------------------
\begin{document}
\frontmatter      % Begin Roman style (i, ii, iii, iv...) page numbering

% Set up the Title Page
\title  {COMP-9710A Master Project Thesis}
\authors  {\texorpdfstring
            {\href{theo.de-framond@insa-lyon.fr}{Theo DE FRAMOND}}
            {Theo DE FRAMOND}
            }
\addresses  {\groupname\\\deptname\\\univname}  % Do not change this here, instead these must be set in the "Thesis.cls" file, please look through it instead
\date       {\today}
\maketitle
%% ----------------------------------------------------------------

\setstretch{1.3}  % It is better to have smaller font and larger line spacing than the other way round

% Define the page headers using the FancyHdr package and set up for one-sided printing
\fancyhead{}  % Clears all page headers and footers
\rhead{\thepage}  % Sets the right side header to show the page number
\lhead{}  % Clears the left side page header

\pagestyle{fancy}  % Finally, use the "fancy" page style to implement the FancyHdr headers

%% ----------------------------------------------------------------
% Declaration Page required for the Thesis, your institution may give you a different text to place here
\Declaration{}

\addtocontents{toc}{\vspace{1em}}  % Add a gap in the Contents, for aesthetics

I, Theo DE FRAMOND, declare that this thesis titled, `Functional testing and qualification of the Serval Mesh Extender' and the work presented in it are my own. I confirm that:

\begin{itemize} 
\item[\tiny{$\blacksquare$}] This work was done wholly or mainly while in candidature for a research degree at this University.
 
\item[\tiny{$\blacksquare$}] Where any part of this thesis has previously been submitted for a degree or any other qualification at this University or any other institution, this has been clearly stated.
 
\item[\tiny{$\blacksquare$}] Where I have consulted the published work of others, this is always clearly attributed.
 
\item[\tiny{$\blacksquare$}] Where I have quoted from the work of others, the source is always given. With the exception of such quotations, this thesis is entirely my own work.
 
\item[\tiny{$\blacksquare$}] I have acknowledged all main sources of help.
 
\item[\tiny{$\blacksquare$}] Where the thesis is based on work done by myself jointly with others, I have made clear exactly what was done by others and what I have contributed myself.
\\
\end{itemize}
 
\clearpage  % Declaration ended, now start a new page

%% ----------------------------------------------------------------
% The "Funny Quote Page"
\pagestyle{empty}  % No headers or footers for the following pages

\null\vfill
% Now comes the "Funny Quote", written in italics
\textit{``Communications should not just be for the geographically, financially otherwise fortunate — for it is the unfortunate who need it most.''}

\begin{flushright}
Serval
\end{flushright}

\vfill\vfill\vfill\vfill\vfill\vfill\null
\clearpage  % Funny Quote page ended, start a new page
%% ----------------------------------------------------------------

% The Abstract Page
\addtotoc{Abstract}  % Add the "Abstract" page entry to the Contents
\abstract{
\addtocontents{toc}{\vspace{1em}}  % Add a gap in the Contents, for aesthetics

This paper is the thesis of my Master Project COMP9710A in Flinders University, School of Computer Sciences as an exchange student from France. It explains all the work, tasks and experiments I have done during my project. The remainder of this content concerns the perspectives and the motivations of such a project and also what I have retained about it.\\
My project takes place in the humanitarian and open source project called Serval. Serval Project purpose is to providing means of communication to people in the incapacity of having cellular coverage. To this end they have developed a smart-phone application and a special smart antenna called the Mesh Extender. My role here is to write automated tests to make sure these Mesh Extender are ready for their next use. 
\par
Keywords : Serval Project, Testing, Mesh Extender, Emergency Communications, Automatic Tests, Servald, Expect, Master Project. 

}

\clearpage  % Abstract ended, start a new page
%% ----------------------------------------------------------------

\setstretch{1.3}  % Reset the line-spacing to 1.3 for body text (if it has changed)

% The Acknowledgements page, for thanking everyone
\acknowledgements{
\addtocontents{toc}{\vspace{1em}}  % Add a gap in the Contents, for aesthetics

I would like to thank the all telecommunication laboratory of Flinders in Tonsley for their participation in the project and for having supported my work and helped me get results of better quality. I am particularly grateful to my supervisor Paul Gardner-Stephen for his patience and support in overcoming numerous obstacles I have been facing through my research. Thanks him for having accepted me in his team.

I would like to thank my fellow students and the ISS of Flinders University for their feedback, cooperation and kind welcome. 

Nevertheless, I am also grateful to my French school INSA Lyon for having given me the opportunity to get here and work in this wonderful country which is Australia. Thanks Isabelle Auge-Blum and the DRI for having organized my student exchange and thanks the jury for having changed their decision regarding this exchange which was at first forbidden for me. 

I would like to thank my friends for accepting nothing less than excellence from me. Last but not the least, I would like to thank my family: my parents and to my sister for supporting me spiritually throughout writing this thesis and my life in general.

\ldots

}
\clearpage  % End of the Acknowledgements
%% ----------------------------------------------------------------

\pagestyle{fancy}  %The page style headers have been "empty" all this time, now use the "fancy" headers as defined before to bring them back


%% ----------------------------------------------------------------
\lhead{\emph{Contents}}  % Set the left side page header to "Contents"
\tableofcontents  % Write out the Table of Contents

%% ----------------------------------------------------------------
\lhead{\emph{List of Figures}}  % Set the left side page header to "List if Figures"
\listoffigures  % Write out the List of Figures


%% ----------------------------------------------------------------
\mainmatter	  % Begin normal, numeric (1,2,3...) page numbering
\pagestyle{fancy}  % Return the page headers back to the "fancy" style

% Include the chapters of the thesis, as separate files
% Just uncomment the lines as you write the chapters

\input{Chapters/Chapter1} 

\input{Chapters/Chapter2}

\input{Chapters/Chapter3}

\input{Chapters/Chapter4}

\input{Chapters/Chapter5} 

\input{Chapters/Chapter6} 

\input{Chapters/Chapter7}

\input{Chapters/Chapter8}


\end{document}  % The End
%% ----------------------------------------------------------------